Bayesian regression facilitates quantitative modelling of cell metabolism

### 2023-10-31 paper/main.qmd
paper update

Posterior predictive checking indicated that our model achieved a good fit
to the simulated reaction and metabolite concentration measurements, as shown
by the graphs in the top row of figure 3. Note that the fit was good for both
training and validation measurements.

Analysis of the posterior distributions for kinetic parameters indicated that
these are highly correlated. The marginal posterior distributions for most
kinetic parameters did not shrink significantly compared with the corresponding
marginal prior distributions, even though these parameters’ joint posterior
distribution contained enough information to make accurate out of sample
predictions. In some cases, there were two-dimensional correlations such
as the one shown in the bottom left of figure 3; in this case the marginal
distribution of the two parameters is roughly banana shaped. More commonly,
however, two-dimensional pair plots were insufficient to reveal the underlying
correlation structure, as seen in the bottom-right plot in figure 3. This does
not mean that the parameters were uncorrelated, but rather that the correlations
involve more than two parameters.

@@

>>>>

Posterior predictive checking indicated that our model achieved a good fit to
the simulated reaction and metabolite concentration measurements, as shown by
the graphs in the top row of figure @fig-posterior.

Analysis of the posterior distributions for kinetic parameters indicated that
these are highly correlated. The marginal posterior distributions for most
kinetic parameters did not shrink significantly compared with the corresponding
marginal prior distributions, even though these parameters’ joint posterior
distribution contained enough information to make accurate out of sample
predictions. In some cases, there were two-dimensional correlations such as
the one shown in the bottom left of figure @fig-posterior; in this case the
marginal distribution of the two parameters is roughly banana shaped. More
commonly, however, two-dimensional pair plots were insufficient to reveal the
underlying correlation structure, as seen in the bottom-right plot in figure
@fig-posterior. This does not mean that the parameters were uncorrelated, but
rather that the correlations involve more than two parameters.

@@

::: {#fig-posterior layout-ncol=1}

![](../figures/posterior.png)
